\subsection{{Data Science Intern} \hfill Feb 2023 – Mar 2023}
\subtext{1Stop.ai \hfill Remote}
\begin{itemize}
\item \textbf{Hate Speech Detection:} Engineered a robust ML model utilizing TF-IDF and word embeddings (Naive Bayes, SVM, Deep Learning) to classify harmful content, optimizing for high precision and F1-score.
\item \textbf{SMS Spam Classification:} Orchestrated a spam detection model utilizing text mining (tokenization, stemming) and algorithms like Logistic Regression and Random Forest, handling imbalanced datasets effectively to minimize false positives.
\item Applied advanced statistical modeling and machine learning techniques to solve complex business problems, communicating actionable insights to stakeholders.
\end{itemize}

\subsection{{Cyber Security Intern} \hfill Sept 2023 - Oct 2023}
\subtext{Rinex \hfill Remote/Hybrid}
\begin{itemize}
\item Secured Grade A+ in the Cyber Security and Ethical Hacking Course.
\item \textbf{Key Projects:} Architected a Network Scanner for vulnerability identification, engineered a MAC Changer for security assessments, and developed a Keylogger Master for ethical system analysis.
\item Executed comprehensive security research, vulnerability assessments, and malware debugging protocols.
\end{itemize}

\subsection{{Web Development Intern} \hfill Feb 2024 - Mar 2024}
\subtext{Worinwell \hfill Remote}
\begin{itemize}
\item Mastered "Web Development with CSS3 and HTML5" curriculum, applying best practices in responsive design.
\item \textbf{Key Project:} Developed a high-performance single-page e-commerce website, ensuring full responsiveness and adherence to modern UI/UX design standards.
\item Optimized front-end development workflows, ensuring cross-browser compatibility and enhanced user experience.
\end{itemize}
