\subsection{{Customer Trends Analysis} \hfill Python, PowerBI, SQL}
\begin{itemize}
\item Conducted comprehensive analysis of customer behavior patterns to uncover actionable retention insights using advanced statistical methods.
\item Developed predictive models to identify at-risk customers, resulting in data-driven strategies for improved retention rates.
\end{itemize}

\subsection{{Crypto Currency Analysis} \hfill Power BI}
\begin{itemize}
\item Designed a dynamic Power BI report analyzing cryptocurrency market trends and price volatility, utilizing DAX for complex calculations.
\item Visualized asset performance over time to provide actionable investment insights and support strategic decision-making.
\end{itemize}

\subsection{{Secure Data Destruction for IT Asset Disposition} \hfill Python, System Programming}
\begin{itemize}
\item Designed a sustainable system for data center repurposing and e-waste reduction, aligning with green computing standards.
\item Implemented rigorous software-based sanitization protocols for hardware reuse to ensure absolute data security.
\item Developed a component-level Wipe Method Visualizer to demonstrate destructive vs. non-destructive sanitization techniques.
\end{itemize}

\subsection{{ThrottleHub - Game Center Management System} \hfill React, Supabase}
\begin{itemize}
\item Engineered a comprehensive admin dashboard for game center operations, overseeing real-time booking, inventory, and financial tracking.
\item Integrated Supabase for secure, scalable authentication and real-time database management.
\item Developed advanced analytics modules for income channel tracking and store performance visualization, enhancing operational visibility.
\end{itemize}

\subsection{{Machine Learning Model for Stress Detection} \hfill Python, ML, Google Colab}
\begin{itemize}
\item Developed a high-accuracy machine learning model for stress detection using ECG signals, leveraging the WESAD dataset.
\item Executed rigorous data preprocessing, feature engineering, and hyperparameter tuning to optimize model performance.
\end{itemize}

\subsection{{Smart Traffic System} \hfill Python, Google Colab}
\begin{itemize}
\item Engineered a smart traffic management system for four-way junctions, featuring centralized control for efficient traffic flow optimization.
\item Deployed as a centralized executable, ensuring maintainability and scalability through Google Colab integration.
\end{itemize}

\subsection{{Cleanware Website} \hfill TypeScript, HTML, CSS}
\begin{itemize}
\item Developed a responsive frontend for a professional cleaning services platform using TypeScript, prioritizing performance and accessibility.
\item Implemented modern UI/UX design principles to ensure fast load times and seamless user interaction.
\end{itemize}
